---
title: "Useful Distributions"
author:
  - name: "Tomasz Woźniak"

execute:
  echo: true
  
bibliography: references.bib
---

> **Abstract.** This document includes useful information about statistical distributions and how to use them in Macroeconometrics. 
>
> **Keywords.** standard normal

# A Standard Normal Distribution

This is a distribution for a real-values random variable $x$ with the expected value equal to 0 and the variance equal to 1. The pdf has the form of
\begin{align}
x\sim\mathcal{N}(0,1) = \frac{1}{\sqrt{2\pi}}\exp\left\{-\frac{1}{2}x^2 \right\}
\end{align}

It is an important one in Macroeconometrics and Bayesian inference because random draws from this distribution are used to provide random draws from other distributions.

To sample `r N = 10` random draws in **R** use the **base** package `rnorm` function:
```{r}
set.seed(1)
rnorm(N)
```
A much faster sampler is provided in package **RcppZiggurat**:
```{r}
RcppZiggurat::zsetseed(1)
RcppZiggurat::zrnorm(N)
```
The speed comparison of sampling 1000 draws:
```{r}
microbenchmark::microbenchmark(
  base = rnorm(1000),
  rcpp = RcppZiggurat::zrnorm(1000)
)
```




## References {.unnumbered}